Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-01-05 Manuscript/HI_Model_ms.Rmd
updated manuscript files

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Natural climate solutions are defined as conservation and land management efforts aimed at enhancing carbon storage in natural biological reservoirs [@griscom_natural_2017]. A growing number of sub-national jurisdictions have set goals to achieve carbon neutrality by mid-century, and plan to incorporate natural climate solutions because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. However, effective implementation is complicated by the considerable uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale.

@@

Hawaii was the first U.S. state to enact legislation supporting commitments and goals of the Paris climate agreement.

>>>>

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Natural climate solutions, defined as conservation and land management efforts aimed at enhancing ecosystem carbon storage [@griscom_natural_2017], are appealing because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. A growing number of sub-national jurisdictions plan to incorporate natural climate solutions as part of a suite of emissions reduction efforts to achieve carbon neutrality by mid-century. However, uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale, complicates efforts to effectively implement natural climate solutions.

@@

Hawaii was the first U.S. state to enact legislation supporting commitments and goals of the Paris climate agreement. Specifically, Hawaii passed Act
